---
title: "Exponential Distribution"
author: "Iulia Zidaru"
date: "16 Aug 2016"
output: pdf_document
---

## Overview
In this project I investigate the exponential distribution in R and compare it with the Central Limit Theorem. 

## Simulations
The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter.
We generate some random samples to see how the distribution looks like.

```{r}
set.seed(5)
lambda <- .2
par(mfrow=c(2,2))
hist(rexp(10, lambda))
hist(rexp(100, lambda))
hist(rexp(1000, lambda))
hist(rexp(10000, lambda))
```

## Sample Mean versus Theoretical Mean

The distribution of 1000 averages of 40 exponentials.
```{r}
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(40, 0.2)))

```

```{r}
sampleMean <- mean(mns)
teoreticalMean <- 1/0.2
sampleMean
teoreticalMean
```

Conclusion: The mean of the simulated samples is close to theoretical mean.

## Sample Variance versus Theoretical Variance

```{r}
sampleVar <- var(mns)
teoreticalVar <- ((1/0.2)/sqrt(40))^2
sampleVar
teoreticalVar
```

Conclusion: The variance of the simulated samples is close to theoretical variance.

## Distribution

```{r}
library(ggplot2)
data <- as.data.frame(mns)

ggplot(data = data, aes(x=mns)) + 
         geom_histogram(aes(y=..density..), binwidth=.25, col="black") +
         geom_vline(aes(xintercept=mean(mns),colour="red")) +
         geom_text(aes(x=mean(mns),label="\nsample mean",y=0.2),colour="black",angle=90)+
         xlab("Averages of the distribution") + ylab("Density")+
         ggtitle("Figure 1: Distribution of the averages of \n40 random exponentials (1000 simulations)") +
         theme(legend.position="none") +
         stat_function(fun=dnorm,args=list(mean=5,sd=sd(mns)))

```

Conclusion: The distribution is standard normal.