---
title: "ToothGrowth Inferential Data Analysis"
author: "Iulia Zidaru"
date: "18 Aug 2016"
output: pdf_document
---

## Load the ToothGrowth data

```{r}
library(ggplot2) 
data(ToothGrowth)
```

## Provide a basic summary of the data and perform some basic exploratory data analyses

```{r}
str(ToothGrowth)
summary(ToothGrowth)
dim(ToothGrowth)
head(ToothGrowth)
tail(ToothGrowth)

qplot(supp,len,data=ToothGrowth, facets=~dose, main="Tooth growth of guinea pigs", ylab="Tooth length") + geom_boxplot(aes(fill = supp))

qplot(dose,len,data=ToothGrowth, facets=~supp, main="Tooth growth of guinea pigs", ylab="Tooth length") + geom_boxplot()
```


## Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

```{r}
t.test(ToothGrowth$len, ToothGrowth$dose, paired=T, var.equal=T, alt="two.sided")
```

## State your conclusions and the assumptions needed for your conclusions.

As the dose is higher, the lenght of the tooth is higher. OJ supplement produces higher growth than VJ suplement.